---
title: Replication of 'Data quality of platforms and panels for online behavioral
  research' by Peer et al. (2021, Behavior Research Methods)
author: "Kimia Saadatian (kimia@stanford.edu)"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: no
  pdf_document:
    toc: yes
    toc_depth: '3'
  word_document:
    toc: yes
    toc_depth: '3'
---

<!-- Replication reports should all use this template to standardize reporting across projects.  These reports will be public supplementary materials that accompany the summary report(s) of the aggregate results. -->

## Introduction

### Justification for choice of study

I will be replicating a study by Peer et al. (2021), which compared data quality (attention, comprehension, reliability and honesty) between multiple sites used for online participant recruitment: Amazon MTurk, CloudResearch (formerly TurkPrime) and Prolific.

### Anticipated challenges

As of right now, I do not anticipate running into any challenges in replicating the results from the original study.

### Links

Project repository: https://github.com/psych251/saadatian2021.git

Survey preview: https://ucbpsych.qualtrics.com/jfe/preview/SV_cSKr5voz0akZ7P8?Q_CHL=preview&Q_SurveyVersionID=current

Project OSF: https://osf.io/qw4sf/?view_only=49333769f6464316a805d48e8cd1d5ca

Original paper: https://github.com/psych251/saadatian2021/blob/3c2eeb3b8a352c51dea439f7878b2ab95f67acff/original-paper/Peer%20et%20al.%20(2021).pdf

Original study's OSF: https://osf.io/342dp/

## Methods

### Power Analysis

Main analysis I am replicating is "We found statistically significant differences between the sites on [overall data quality score], F(2, 1458) = 129.4, p < .001, which showed higher scores for Prolific and CR (M = 5.87, 5.78, SD = 1.0, 1.1, respectively) compared to MTurk (M = 4.55, SD = 1.9)).

For a power of 0.95, I will need 43 Participants in each group. However, to get precise estimates of the differences, I will recruit 100 participants from each of the three platforms (Mturk, CloudResearch, and Prolific), adding to a total of 300 participants.



### Planned Sample

I will recruit participants on Amazon MTurk, CloudResearch, and Prolific. Participants must be U.S. residents age 18 or above. Similar to the original study, I will exclude participants who do not complete all of the study.

"We recruited 500 participants from each platform
(MTurk, CR, and Prolific), who reported residing in the
United States, in March 2021. Participants were paid 1.5
USD on CR and MTurk and 1.1 GBP on Prolific plus a bonus
of up to 0.5 USD/GBP. We applied data quality prescreening
filters on all sites by restricting the study to participants with at
least 95% approval rating and at least 100 previous submissions; on CR we also used the site setting to “block low data
quality workers.” We excluded participants on Prolific who
completed the previous study on Prolific and participants on
CR who completed the previous study on CR or MTurk.
However, because our study had to be posted twice on
MTurk (once through our MTurk account and once through
our CR account), 39 participants completed the study twice,
and we removed their later submission (although they were
still paid for their submissions). The final sample thus included 1461 participants who completed the study. Table 4 presents the samples. Additional demographics can be found in
the Appendix."

### Materials

"1. Attention is measured using two attention-check questions. The first asks participants to answer "six" and "three" to two items regardless of their actual
preference (other responses are coded as failures); the second is an item within a scale worded "I currently don't pay attention to the questions I'm being
asked in the survey" (response other than "strongly disagree" is coded as a failure)
2. Comprehension is examined through the oral summaries of instructions to two tasks. The first task asks participants to identify faces in a picture, but
includes an instruction to only report zero; the second includes instructions for the "Matrix task" (Mazar et al., 2008). Two raters will code the oral
responses independently and blind to the origin of the participant. We will consider an answer correct if both readers agree it is correct, and will apply a
third reader to any answer with splits.
3. Reliability will be measured using Cronbach's alpha measure for the Need for Cognition scale.
4. Honesty will be measured using an online version of the Matrix task (Mazar et al., 2008) that will include two unsolvable matrices. Reporting solving any
of these two problems will be coded as a dishonest response. Additionally, we will examine whether participants lie about their eligibility for a future study
by asking them to indicate if they want to be invited to a study that samples participants of their own gender but whose age will be described as 5-10 years
above the age participants reported in the beginning of the study.

In addition we will examine drop-out rates, duration for completing the survey, overall response time and speed between sites, differences in NFC,
demographics, and patterns of usage of the site (main purpose, frequency of usage, number of submissions and approval ratings, usage of other sites), and
we will also ask participants to report did they complete a study similar to this study in the last months."

### Procedure	

"Participants were invited to complete a survey on
individual differences in personal attitudes, opinions, and behaviors. All participants began the survey by answering demographic questions, followed by the data quality measures
described below. Participants finished the survey by answering questions related to their usage of the online platform
including how often they use the site, for what purposes,
how much they earn in an average week, their percent of
approved submissions (responses that participants submit
and are approved by the researcher), and how often (if at all) they use other sites."


"We will apply data quality filters on all three sites in the following scheme:
1) MTurk - only workers who have completed 100 submissions or more and 95% of those submissions were approved.
2) CloudResearch - only workers who have completed 100 submissions or more and 95% of those submissions were approved + the default setting on CloudResearch of "block low data quality workers"


I will be replicating their study 2, which originally averaged around 9.8 minutes long (SD = 5.2). Participants will be paid $1.50 to participate in this ~10 minutes-long survey.

### Analysis Plan

I plan to follow the same analyses that were conducted in the original study.

The main analysis I am replicating is from study 2, where Peer et al. (2021) found higher data quality scores for data obtained from Prolific and CloudResearch (M = 5.87, 5.78, SD = 1.0, 1.1, respectively) compared to MTurk (M = 4.55, SD = 1.9; F(2, 1458) = 129.4, p < .001).


In order to compute the overall data quality score, the original authors "used chi-square tests to examine differences in the rates of attention, comprehension and dishonesty. They also computed average scores for (across the items per aspect) and compared them between sites using ANOVA and regression analyses. They tested for differences between reliability coefficients using Hakistan & Whalen (1976) method. Lastly, they computed an overall composite score of data quality (based on the average scores of attention, comprehension and dishonesty) and compare them between sites using ANOVA and regression."

The composite Data Quality score ranged from 0 to 7 (M = 5.41; SD = 1; Med = 6) 
Overall data quality composite scores ranked from highest to lowest were:
Prolific (M = 5.87, SD = 1.0) 
CR ( M = 5.78, SD =  1.1) 
MTurk (M = 4.55, SD = 1.9)

They found statistically significant differences between the sites on Overall Data Quality Score, F(2, 1458) = 129.4, p < .001

Post hoc tests with Bonferroni correction:

differences between Prolific and MTurk p < .001 
differences between CR and MTurk p < .001 
difference between CR and Prolific  p = 0.91. 


### Differences from Original Study
I do not anticipate any deviations from the original analysis plan at this stage.


### Methods Addendum (Post Data Collection)

#### Actual Sample

#### Differences from pre-data collection methods plan


## Results


### Data preparation

Data preparation following the analysis plan.

```{r, echo=FALSE}
### Fixing error with knitting
#### RMarkdown v1 used error = TRUE by default, but RMarkdown v2 uses error = FALSE.

knitr::opts_chunk$set(error = TRUE)
```

```{r}
###Data Preparation
##### Starting a Script #####

  # Clear environment
    rm(list=ls())

  # Checking working directory
    getwd()

  #### Loading in data ####
    
    # Load csv
      dat <- read.csv("pilotB-replication.csv",
                       na.strings="NA", strip.white=TRUE)

####Load Relevant Libraries and Functions
    library(tidyverse)
    library(dplyr)
    library(car)
    library(ggplot2)

##### Looking at your data #####
      
  #### Identifying problems ####
      
    # Finding the number of duplicate cases
      # WARNING: These do not include the first instance of the duplicated value.
      length(dat$id) - length(unique(dat$id))
      
    # Finding rows of duplicate cases. 
      # WARNING: These do not include the first instance of the duplicated value.
      which(duplicated(dat$column))
      
  #### Looking at your whole dataset ####
      
      # Get names, data types, and first 10 data points of every column 
        str(dat)
      
      # Get a list of column names of your data (in order)
        colnames(dat)
        
      # Show the first five rows of your data. 
        head(dat)
        
      # Show the whole dataset in the data viewer
        View(dat)
        
      # Get the number of rows in your dataset
        nrow(dat)
      
      # Get the number of columns in your dataset
        ncol(dat)
        
      # Looking at a random set of 10 observations
        sample_n(dat, 10)
      
      # Look at whole dataframe
        library(summarytools)
        view(dfSummary(dat))

 #### Looking at columns ####
      
    # View the levels of a factor and their order
      levels(dat$cond)
      
    # View a summary of your data (count of each factor level for factors, numeric summary for numeric)
      summary(dat)
    
  #### Summary statistics ####
   # Getting summary values with the standard error. Good for plotting. 
      # Rmisc package
      datsum <- summarySE(dat, eachmeasure ="value",
          groupvars=c("platform","variable"))

#### Data exclusion / filtering
  #### Removing unwanted data ####
      
    # Omitting rows with NAs
      data <- na.omit(dat)
    

#### Prepare data for analysis - create columns etc.
      
      filtered_data %>% 
  group_by(sample) %>% 
  summarize(avg_sales = mean(sales))
```

### Confirmatory analysis

The analyses as specified in the analysis plan.  

I will report differences between sites on each data quality measure and then aggregate those findings to a composite score of data quality, reporting differences across all sites.

ATTENTION
(originally : ACQs, χ2(4) = 548.48, 203.56, p < .001. )

```{r}
recode firstacq1 so that :
   pass if  acq1 = "6" ; fail ifelse
recode firstacq2 so that :
   pass if acq2 = "3" ; fail ifelse
firstacq <- c(acq1, acq2)

recode secondacq so that : 
    pass if nfc12 = '1' ; fail ifelse
```


COMPREHENSION
(originally : χ2(4) = 152.4, p < .001 )

```{r}
Have 2 coders code any response that suggested a minimum level of understanding as indicating comprehension and only flag responses as incorrect if they were undoubtedly illegible. Responses that are flagged by both raters will be coded as incorrect answers.
  
manually code open responses to firstcomprehension1
manually code open responses to secondcomprehension1
```

HONESTY
(originally :  χ2(4) = 153.44, p < .001 )

```{r}
fifth problem was unsolvable and the original investigators focused on this problem’s reports as a measure of dishonesty3.
```


RELIABILITY
(originally : )

```{r}
"Reliability was measured using the NFC scale (Cacioppo et al., 1984), which measures the extent to which respondents like to engage in and enjoy thinking.
The negatively worded items were recoded before analyses.
We chose these scales because they have been found as highly reliable and were validated across extensive studies previously."

nfc<- c(nfc1 to nfc11, nfc13 to nfc18)
 recode reversescored items
```

OVERALL DATA QUALITY SCORES
(originally: "The score gave participants a value between 0 and 5, showing whether they passed one or both ACQs, answered correctly one or two comprehension questions, and did not claim to have solved the unsolvable problem. The correlations between the five measures ranged between 0.16 and 0.43, all p < .01, but the overall composite score should not be considered as measuring the same construct. Rather, it is used here as a multifactorial measure that attests to the overall general level of data quality")

```{r}
dataquality <- c(acq1,acq2,comprehension1,comprehension2,honesty)
```

LOOKING AT ALL MEANS ON EACH PLATFORM
```{r}
dat %>% 
  group_by(platform) %>%
  summarize(avgvariable = mean(variable, na.rm = T)) # the na.rm tells R to ignore NA values
```


COMPARING DATA QUALITY ACROSS THE THREE GROUPS
```{r}
# Compute one-way ANOVA
difone <- aov(mturk ~ prolific, data = dat)
diftwo <- aov(mturk ~ cloudresearch, data = dat)
difthree <- aov(cloudresearch ~ prolific, data = dat)
# Summary of one-way ANOVA
summary(difone)
summary(diftwo)
summary(difthree)
```

*Side-by-side graph with original graph is ideal here*

-----

### Exploratory analyses


## Discussion

### Summary of Replication Attempt

-> Open the discussion section with a paragraph summarizing the primary result from the confirmatory analysis and the assessment of whether it replicated, partially replicated, or failed to replicate the original result.  

### Commentary

-> dd open-ended commentary (if any) reflecting (a) insights from follow-up exploratory analysis, (b) assessment of the meaning of the replication (or not) - e.g., for a failure to replicate, are the differences between original and present study ones that definitely, plausibly, or are unlikely to have been moderators of the result, and (c) discussion of any objections or challenges raised by the current and original authors about the replication attempt.  None of these need to be long.
